%  
% #INFO: An example of writing Thesis with LaTeX using `mcidoc'
%
% Copyright (C) 2023-2026 -DTMc
%
% COPYRIGHT NOTICE:
% -----------------
% It may be distributed and/or modified under the conditions of the LaTeX Project Public
% License (LPPL), either version 1.3c of this license or (at your option) any later version.
% The latest version of this license is in the file
%
% https://www.latex-project.org/lppl.txt
% 
% This file is part of `mcidoc' and all files in that bundle must be distributed together.
% 
% ---------------------------------------------------------------------------------------------
%  
\documentclass[state=Thesis]{../mcidoc}
%
% DOCUMENT CONFIGURATION ----------------------------------------------------------------------
%
% As stated in the `mcidoc' documentation, `\SetMCI' is the primary way in which the document
% is changed into a form that is usable to the user. For more information about which options
% are available for configuration, please visit the documentation at
%
% LINK: https://dtmc0945.github.io/C-MCI-LaTeX-Class-mcidoc/
% 
\SetMCI{%
  % 
  % GLOBAL SETTINGS -- ------------------------------------------------------------------------
  % LINK: https://dtmc0945.github.io/C-MCI-LaTeX-Class-mcidoc/Global-Options.html
  % 
  StudentName    = {%
    Name = {Colin Stevens}
  },%  
  StudentID      = {2314808},
  Degree         = MSc,  
  Language       = EN,  
  Department     = MECH, 
  %    
  % -------------------------------------------------------------------------------------------
  %   
  Thesis = { %        
    Title          =  {On the Study of Different \& Rotor Geometry Configuration
                      for use in High-Speed Induction Motors},
    StudyProgram   = {Mechatronik, Design \& Innovation},
    %%  
    Supervisor     = {%  
      %% Company = {Ministry of Typography},
      Prefix  = {Prof.},  
      Name    = {Colin Stevens}, 
      Postfix = {Ph.D}, 
    },%          
    %%        
    % Reviewer     = {%  
    %   Prefix     = Dan,
    %   Name       = Colin Stevens,
    %   Postfix    = Esh.,  
    % },%    
    % Double-Degree  = {  
    %   Institution     = {ASU},
    %   Student-Number  = {11111111111}, 
    %   Supervisor     = {%  
    %     Prefix  = {Prof.},   
    %     Name    = {Colin Stevens},
    %     Postfix = {},
    % },%       
    % },       
    %%  
    Embargo        = {31.07.2031},
    Location       = {Istanbul},
    Date           = {21.05.2002},
    %%     
    Bibliography   = {%     
      State        = set,  
      Location     = {references.bib},  
      Print        = set,     
    },        
  },     
  Report = {
    Title          = {On the Study of Different \& Rotor Geometry Configuration
                      for use in High-Speed Induction Motors},
    Lecture        = {Drive Technologies},
    },
 }                                               
%   
% CUSTOM COMMANDS -----------------------------------------------------------------------------
% 
% Please enter any custom command/packages you require here for easy tracking and easy
% maintenance.
% 
\RequirePackage{siunitx}
\RequirePackage{tabularx} 
\RequirePackage{pgfplots}
\RequirePackage{array, booktabs, multirow} 

\makeatletter  
\RequirePackage[
backend = bibtex,  
style   = ieee, 
]{biblatex}

% Here we add our file where we store our references.
\bibliography{\Thesis@Bibliography@Location} 
\makeatother   

% ABSTRACTS & ACKNOWLEDGMENTS -----------------------------------------------------------------
 


\begin{Abstract}{EN}    
        
  Abstracts contain most of the following kinds of information in brief form. The body of your
  paper will, of course, develop and explain these ideas much more fully. As you will see in
  the samples below, the proportion of your abstract that you devote to each kind of
  information—and the sequence of that information—will vary, depending on the nature and genre
  of the paper that you are summarizing in your abstract. And in some cases, some of this
  information is implied, rather than stated explicitly. The Publication Manual of the American
  Psychological Association, which is widely used in the social sciences, gives specific
  guidelines for what to include in the abstract for different kinds of papers—for empirical
  studies, literature reviews or meta-analyses, theoretical papers, methodological papers, and
  case studies.
       
\end{Abstract}     
          
\begin{Abstract}{DE}    
      
  Abstracts contain most of the following kinds of information in brief form. The body of your
  paper will, of course, develop and explain these ideas much more fully. As you will see in
  the samples below, the proportion of your abstract that you devote to each kind of
  information—and the sequence of that information—will vary, depending on the nature and genre
  of the paper that you are summarizing in your abstract. And in some cases, some of this
  information is implied, rather than stated explicitly. The Publication Manual of the American
  Psychological Association, which is widely used in the social sciences, gives specific
  guidelines for what to include in the abstract for different kinds of papers—for empirical
  studies, literature reviews or meta-analyses, theoretical papers, methodological papers, and
  case studies. 
    
\end{Abstract}     

\begin{Acknowledgments}  

  I extend my deepest gratitude to my supervisor, Professor Jane Smith, for her unwavering
  support and insightful critiques throughout my research journey. Her deep commitment to
  academic excellence and meticulous attention to detail have significantly shaped this
  dissertation. I am equally thankful to the members of my thesis committee, Dr. John Doe and
  Dr. Emily White, for their constructive feedback and essential suggestions that enhanced the
  quality of my work.

  My appreciation also goes to the faculty and staff in the Department of Biology at University
  College London, whose resources and assistance have been invaluable. I would also like to
  acknowledge my peers for their camaraderie and the stimulating discussions that inspired me
  throughout my academic journey. Their collective wisdom and encouragement have been a
  cornerstone of my research experience.

  Finally, my sincere thanks to the technical staff whose expertise in managing laboratory
  equipment was crucial for my experiments. Their patience and readiness to assist at all times
  have left a profound impact on the completion of my project.
  
\end{Acknowledgments}

\begin{document} % ############################################################################
 
% NOTE ----------------------------------------------------------------------------------------
% Your primary thesis content should go here and should follow structure befitting of a
% scientific report and should be written in a scientific format.
%
% For more information please look at MCI guidelines on how it should be done.
% ---------------------------------------------------------------------------------------------
     
% Include Chapter - introduction  
\include{chapter/introduction.tex}
% Include Chapter - literature survey  
\include{chapter/literature-survey.tex}
% Include Chapter - Finite Element Method
\include{chapter/Finite-Element-Method}   
% Include Chapter - Conclusion and Future Work
\include{chapter/Conclusion-and-Future-Work} 
                            
% NOTE ----------------------------------------------------------------------------------------
% Add as many chapters as you see fit for your content. For easy legibility and dynamic
% adjustment of content try to write a `file per chapter' such as the example shown above.
% ---------------------------------------------------------------------------------------------
  
\end{document} % ##############################################################################
%   
%%% Local Variables: 
%%% coding: utf-8 
%%% mode: latex
%%% TeX-command-extra-options: "-shell-escape"
%%% TeX-master: t
%%% TeX-engine: luatex
%%% End:
% ---------------------------------------------------------------------------------------------
%
% Main-Thesis.tex ends here.
%
                       
